\documentclass[11pt]{amsart}
\usepackage{amssymb,latexsym,amsmath}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{enumitem}

%-----------------------------------------------------------------
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz2pt % Don't report over-full h-boxes if over-edge is small

% \input{../5718---/classinfo/classinfo}
% \input{../5718---/classinfo/math5718macros}
% \graphicspath{{../Figures/}}

%\setlength{\topmargin}{-.3in}
%\setlength{\headheight}{.2in}
%\setlength{\headsep}{.3in}
%\setlength{\oddsidemargin}{0in}
%\setlength{\evensidemargin}{0in}
%\setlength{\textwidth}{6.5in}
%\setlength{\textheight}{8.5in}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------

% \pagestyle{empty}

% \def\quiznum{1}
% \def\printsol{0}
% \def\quizdate{Wednesday,  September 27, 2023}

\begin{document}

\hfill \textbf{Name:\underline{\hspace*{5cm}}}\\
\begin{center}
\textbf{MATH 5718 :: Fall 2023 :: Exam 2}\\
\end{center}
\vspace{.5cm}
\framebox{
\begin{minipage}{\textwidth}
These assumptions hold for all questions unless otherwise specified.\\
\hspace*{.4cm}\begin{minipage}{.9\textwidth}
$\mathbb{F}$ is a commutative field. If $\mathbb{F}$ is prescribed to be $\mathbb{R}$ or $\mathbb{C}$, this will be indicated.\\$(V,+,\cdot)$ is a nonzero vector space over $\mathbb{F}$.\\
$T$ is a linear operator on $V$.
\end{minipage}
\end{minipage}
}

\vspace{.5cm}

\input{exam2_part1.tex}


\newpage
\noindent
{\bf Question 2.} 
Let $T$ be an operator on $V$. 
Let $\lambda$ be an eigenvalue of $T$. Let $x$ be an eigenvector associated to the eigenvalue $\lambda$.
Let $\mu$ be an eigenvalue of $T$. Let $y$ be an eigenvector associated to the eigenvalue $\mu$.
Assume that $\lambda$ and $\mu$ are distinct. Prove that $x, y$ is linearly independent.


\newpage \noindent
{\bf Question 3.} 
Let $V$ be a complex vector space. Let $S$ and $T$ be two operators on $V$ such that $TS = ST$.
\begin{enumerate}[label=(\alph*)]
\item Prove that if $\lambda$ is an eigenvalue of $S$ then the eigenspace of $S$ associated with the eigenvalue $\lambda$,
$E_\lambda$, is invariant under $T$.
\item Prove that $S$ and $T$ have (at least) one common eigenvector.
\end{enumerate}

\newpage \noindent
{\bf Question 4.} 
We consider $\mathcal{M}_2(\mathbb{R})$ the real vector space of the 2-by-2 real matrices. 
We consider the linear operator $f$ on $\mathcal{M}_2(\mathbb{R})$ defined as:

$$
\begin{array}{rcl}
\varphi: \mathcal{M}_2(\mathbb{R})& \rightarrow &\mathcal{M}_2(\mathbb{R}) \\
\left(\begin{array}{cc}a&b\\c&d\end{array}\right) &\mapsto &
\left(\begin{array}{cc}d&-b\\-c&a\end{array}\right)\\
\end{array}
$$
Give eigenvalues and eigenvectors (so eigencouples) for $f$. 
In addition
say whether $f$ is diagonalizable of not. If $f$ is diagonalizable, give a basis of eigenvectors.


\newpage \noindent
{\bf Question 5.} 
Let $V$ be a nonzero finite dimensional vector space and $T$ an operator on $V$. 
We define
$$
\begin{array}{rcl}
\varphi: \mathcal{L}(V)& \rightarrow &\mathcal{L}(V) \\
T &\mapsto &TS\\
\end{array}
$$
\begin{enumerate}[label=(\alph*)]
\item Suppose that $\lambda$ is an eigenvalue of $T$.
\begin{enumerate}[label=(\alph*)]
\item
 Prove that $\lambda$ is also an eigenvalue of $\varphi$.
\item
The associated eigenspace (of $T$), $E_\lambda$, has dimension $k$.
What is the dimension of the eigenspace (of $\varphi$), $F_\lambda$, associated with the eigenvalue $\lambda$.
\end{enumerate}
\item Prove that if $T$ is diagonalizable, so is $\varphi$.
\end{enumerate}



\end{document}
